---
title: "South African Data Visualisation"
author: "Umar Ahmad"
date: "6/16/2021"
output: word_document
---
# Introduction to the Dataset

Working with the south african dataset to run all the analyses. 

1. Create a new project. Make sure you put it somewhere you'll be able to find it again later!

2. Import the dataset "dataset.csv" from data folder in your project 

3. Create a new RMarkdown document where all of the analyses will be carried out

```{r}
library(tidyverse) ## because tidyverse
library(skimr) ## looking at the data
library(ggpubr) ## for qq plots
library(rstatix) ## for shapiro_test that is pipe-friendly
```

# Importing data

```{r}
library(readr)
dataset <- read_csv("data/dataset.csv")
View(dataset)
```

## Data cleaning. 

```{r}
library(dplyr)
 dat <- dataset %>% 
    rename(year = Year, country = Country, topic = Topic, authors = Authors, 
           no_authors = No_Authors, title = Title, institution = Institution, journal = Journal, african_journal = African_Journal, impact = Impact, citations = Citations, model = Model, genetic = Genetic, research_types = Basic_Clinical, adv_methods = Adv_Methods, plants = Plants, p_name = P_Name, p_use = P_Use, p_success = P_Success, n_affiliations = N_affiliations, international_collab = InternationalCollab) 
 
 ifelse(dat$african_journal=="Yes", 1,0)
```



```{r}
write.csv(dat, "data/data_set.csv")
read_csv("data/data_set.csv")
View(data_set)
```


## Total publication per year for clinical (green) and basic research (black). 

```{r}

```


## Mean citations per annum for clinical (green) and basic research (black). 

```{r}
library(readr)
dataset <- read_csv("data/dataset.csv")
View(dataset)
```

## Mean citations per annum for clinical (green) and basic research (black). 

```{r}
library(readr)
dataset <- read_csv("data/dataset.csv")
View(dataset)
